Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/eval.tex
depend vs u16_depend

The \cc{file} grammar for a ZIP file entry is particularly interesting.
It receives as arguments the file size, checksum, and compression method
of the file from the directory header.  However, this same information
is duplicated in the file entry, so the grammar uses the Nail-supplied
\cc{depend} transform to check whether the two values are equal. Unlike
most other transforms, \cc{depend} does not consume or produce strings; it
only checks that two dependent fields are equal when parsing, and assigns
the value of the second field to the first when generating.  This ensures
that the programmer does not have to worry about inconsistencies when
handling the internal representation of a ZIP file.

>>>>

The \cc{file} grammar for a ZIP file entry is particularly interesting.
It receives as arguments the file size, checksum, and compression method
of the file from the directory header.  However, this same information
is duplicated in the file entry, so the grammar uses the Nail-supplied
\cc{u16\_depend} transform to check whether the two values are equal. Unlike
most other transforms, \cc{u16\_depend} does not consume or produce strings; it
only checks that two dependent fields are equal when parsing, and assigns
the value of the second field to the first when generating.  This ensures
that the programmer does not have to worry about inconsistencies when
handling the internal representation of a ZIP file.
